### 2021-05-20 article/article.tex
update

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real. In Fig.~\ref{fig:flux_ratio}, we study
the flux ratio arising from the introduction of the NSI parameter $\emt$. Fig.~\ref{fig:Pmm_asymmetry} shows the difference $P_{\mu\mu}(\emt>0) - P_{\mu\mu}(\emt<0)$ in the low \si{\GeV} energy range. 
%TODO: maybe plot P_NSI - P_SI instead.

>>>>

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real.

In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} area. Any NSI parameter involving $\mu$ or $\tau$ will dampen this resonance,
with some also shifting the probability in the \SI{100}{\GeV} stationary region.
This `double effect' of both resonance dampening and shifting happens in two cases: either when the parameter shares one channel with a survival probabilitywe have a survival probability
(i.e. $P_{\mu\mu}$ and $\eem$), or when the sectors align (i.e. $\emt$ for $P_{\mu\tau}$). The only exception to this rule is for $P_{\tau\tau}$, 
which due to its near-maximal mixing with the $\mu$ channel displays dampening for $\eem$ even though they share no channel directly. We illustrate
the three different effects in Fig.~\ref{fig:nsi_probs}.

Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the GeV range. Thus, the only impact that 
the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
are met. So except for $P_{ee}$ where the probability is high, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by  $\epsilon_{\alpha\beta}$. Any probabilities $P_{e\beta}$ will
only see a shift in the stationary region, while the two other channels undergo either resonance dampening, or the `double effect'.
\begin{figure}
   \includegraphics[width=0.8\textwidth]{figures/nsi_probs.pdf}
   \caption{The three different effects that the off-diagonal NSI parameters have in the \si{\GeV} range.}\label{fig:nsi_probs}
\end{figure}
